### 2013-01-21 Docs/analysis/analysis.tex
renname docs Docs
update path for python plotting routines

\item {\tt fIDLdump.f90}, {\tt fIDLdump3d.f90}

  Create a binary file containing a uniformly gridded, single variable
  from a plotfile.  This is can then be read into IDL using the routines
  in {\tt fParallel/scripts/idlbl/}.

@@

As a concrete example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt AmrPostprocessing/F\_Src/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/AmrPostprocessing/F_Src/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

>>>>

@@

As a concrete example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt AmrPostprocessing/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/AmrPostprocessing/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

### 2013-01-21 Docs/managing_jobs/managingjobs.tex
add a label
update path for python plotting routines

@@

Then edit your {\tt .bashrc.ext} file to set the {\tt PYTHONPATH} to
the {\tt python\_plotfile} directory, e.g.:
\begin{verbatim}
export PYTHONPATH="/global/homes/z/zingale/AmrPostprocessing/F\_Src/python_plotfile"
\end{verbatim}
%
and set the {\tt PATH} to that directory,
\begin{verbatim}
export PATH="/global/homes/z/zingale/AmrPostprocessing/F_Src/python_plotfile:$PATH"
\end{verbatim}

>>>>

\label{ch:managingjobs}

@@

Then edit your {\tt .bashrc.ext} file to set the {\tt PYTHONPATH} to
the {\tt python\_plotfile} directory, e.g.:
\begin{verbatim}
export PYTHONPATH="/global/homes/z/zingale/AmrPostprocessing/python"
\end{verbatim}
%
and set the {\tt PATH} to that directory,
\begin{verbatim}
export PATH="/global/homes/z/zingale/AmrPostprocessing/python:$PATH"
\end{verbatim}

### 2013-01-21 Docs/visualization/visualization.tex
update path for python plotting routines

{\tt AmrPostprocessing/F\_Src/python\_plotfile} provide some simple commandline
tools for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

The path to {\tt fsnapshot.so} should be included in your {\tt PYTHONPATH}
environment variable.  This can be done by adding:
\begin{verbatim}
export PYTHONPATH="${PYTHONPATH}:/home/user/AmrPostprocessing/F_Src/python_plotfile}
\end{verbatim}
to your {\tt .bashrc}.

>>>>

{\tt AmrPostprocessing/python} provides some simple commandline
tools for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

The path to {\tt fsnapshot.so} should be included in your {\tt PYTHONPATH}
environment variable.  This can be done by adding:
\begin{verbatim}
export PYTHONPATH="${PYTHONPATH}:/home/user/AmrPostprocessing/python}
\end{verbatim}
to your {\tt .bashrc}.
